### 2021-07-08 doc/thesis/chapters/dsp.tex
diagrams

\includepicture [1.3] [0] {Block diagram and signal spectrum of down-conversion.} {bd_down_conversion_spectrum} {img/draw.io/down-conversion-AM-spectrum-and-bd}

@@

The sampling frequency needs to meet the sampling theorem, in order to correctly represent the analog signal.
The sampling theorem, by Nyquist and Shannon mainly consists of the following formula.

\begin{equation}
  f_{s} > 2 \cdot f_{signal}
\end{equation}

@@

\includepicture [0.9] [0] {
  Signal spectrum, explaining the process of down-conversion.\\
  Diagram A) $f_s$ is high enough and thus meets the theorem.\\
  Diagram B) $f_s$ exactly meets the theorem.\\
  Diagram C) $f_s$ is too low and thus creates overlaps of the spectral replicas - aliasing \cite{ThyagarajanK.S2019ItDS}.
} {aliasing_freq_spectrum} {img/sampling-aliasing}

>>>>

\includepicture [1.0] [0] {Block diagram and signal spectrum of down-conversion.} {bd_down_conversion_spectrum} {img/draw.io/down-conversion-AM-spectrum-and-bd}

@@

The sampling frequency needs to meet the sampling theorem, in order to correctly represent the analog signal.
The sampling theorem, by Nyquist and Shannon mainly consists of the following formula.
\begin{equation}
  f_{s} > 2 \cdot f_{signal}
\end{equation}

@@

\includepicture [0.9] [0] {
  Signal spectrum, explaining the process of down-conversion.\\
  Diagram A) $f_s$ is high enough and thus meets the theorem.\\
  Diagram B) $f_s$ exactly meets the theorem.\\
  Diagram C) $f_s$ is too low and thus creates overlaps of the spectral replicas - aliasing \cite{ThyagarajanK.S2019ItDS}.
} {aliasing_freq_spectrum} {img/draw.io/sampling-aliasing}
